High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-08-08 notebooks/mnist.qmd
all coding stuff done

```{julia}
# Hyper:
_retrain = false
_regen = true

@@

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
    model_dict=model_dict,
    wide::Bool = false,
    img_height::Int = img_height,
)

    # Setup:
    Random.seed!(rng)
    if x isa Int
        x = reshape(counterfactual_data.X[:,rand(findall(labels.==x))],input_dim,1)
    end

@@

    ces = Dict()
    for (mod_name, mod) in model_dict
        ce = generate_counterfactual(
            x, target, counterfactual_data, mod, eccco_generator; 
            decision_threshold=γ, max_iter=T,
            initialization=:identity,
            converge_when=:generator_conditions,
        )
        ces[mod_name] = ce
    end
    _plt_order = map(x -> findall(collect(keys(model_dict)) .== x)[1], plt_order)

    # Plot:
    p1 = Plots.plot(
        convert2image(MNIST, reshape(x,28,28)),
        axis=nothing, 
        size=(img_height, img_height),
        title="Factual"
    )

    plts = []
    letters = collect('a':'z')[1:length(ces)]
    _count = 1

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    if wide
        plt = Plots.plot(plts...; size=(img_height*length(plts),img_height), layout=(1,length(plts)))
    else
        plt = Plots.plot(plts...; size=(img_height,img_height))
    end

@@

function MLJFlux.build(b::RobustNetBuilder, rng, n_in, n_out)
	n_hidden, γ = b.n_hidden, b.lipschitz_bound
    _n_hidden = fill(n_hidden,1)
    model_ps = DenseLBDNParams{Float32}(n_in, _n_hidden, n_out, γ; rng)
    chain = Flux.Chain(DiffLBDN(model_ps))
	return chain
end

# Final model:
rob_net = NeuralNetworkClassifier(
    builder=RobustNetBuilder(128, 5.0),
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

>>>>

```{julia}
# Hyper:
_retrain = false
_regen = false

@@

```{julia}
function _plot_eccco_mnist(
    x::Union{AbstractArray, Int}=x_factual, target::Int=target;
    λ=[0.1,0.25,0.25],
    temp=0.1,
    plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"],
    opt = nothing,
    rng::Union{Int,AbstractRNG}=1234,
    T::Int = 100,
    use_class_loss::Bool = true,
    model_dict=model_dict,
    wide::Bool = false,
    img_height::Int = img_height,
    plot_factual::Bool = false,
    kwrgs...,
)

    # Setup:
    Random.seed!(rng)
    if x isa Int
        x_fact = counterfactual_data.X[:,rand(findall(labels.==x))][:,:]
    else
        x_fact = x
    end

@@

    ces = Dict()
    for (mod_name, mod) in model_dict
        ce = generate_counterfactual(
            x_fact, target, counterfactual_data, mod, eccco_generator; 
            decision_threshold=γ, max_iter=T,
            initialization=:identity,
            converge_when=:generator_conditions,
        )
        ces[mod_name] = ce
    end
    _plt_order = map(x -> findall(collect(keys(model_dict)) .== x)[1], plt_order)

    # Plot:
    p1 = Plots.plot(
        convert2image(MNIST, reshape(x_fact,28,28)),
        axis=([], false),
        size=(img_height, img_height),
        title="Factual"
    )

    if plot_factual
        plts = [p1]
    else
        plts = []
    end
    letters = collect('a':'z')[1:length(ces)]
    _count = 1

    for (_name,ce) in collect(ces)[_plt_order]
        _x = CounterfactualExplanations.counterfactual(ce)
        _phat = target_probs(ce)
        _title = "($(letters[_count]))"
        plt = Plots.plot(
            convert2image(MNIST, reshape(_x,28,28)),
            axis=([], false), 
            size=(img_height, img_height),
            title=_title
        )
        plts = [plts..., plt]
        _count += 1
    end
    if wide
        plt = Plots.plot(plts...; size=(img_height*length(plts),img_height), layout=(1,length(plts)), kwrgs...)
    else
        plt = Plots.plot(plts...; size=(img_height,img_height), kwrgs...)
    end

@@

function MLJFlux.build(b::RobustNetBuilder, rng, n_in, n_out)
	n_hidden, γ = b.n_hidden, b.lipschitz_bound
    _n_hidden = fill(n_hidden,2)
    model_ps = DenseLBDNParams{Float32}(n_in, _n_hidden, n_out, γ; rng)
    chain = Flux.Chain(DiffLBDN(model_ps))
	return chain
end

# Final model:
rob_net = NeuralNetworkClassifier(
    builder=RobustNetBuilder(60, 5.0),
    epochs=600,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)
```

@@

```{julia}
_plt_order = [
    "MLP", 
    "MLP Ensemble", 
    "Large Ensemble (n=50)", 
    "LeNet-5",
    "RobustNet",
    "JEM", 
    "JEM Ensemble",
]
plt_additional_models, _, _ces_ = _plot_eccco_mnist(
    plt_order = _plt_order,
    model_dict=large_model_dict,
    wide = true,
    plot_factual = true,
    img_height = 150,
)
display(plt_additional_models)
savefig(plt_additional_models, joinpath(output_images_path, "mnist_eccco_additional.png"))
```

```{julia}
combos = [
    (7,2),
    (0,8),
    (8,3),
    (9,4),
]

plts = [plt_additional_models]

for (factual, target) in combos
    plt, _, _ = _plot_eccco_mnist(
        plt_order = _plt_order,
        model_dict = large_model_dict,
        x = factual,
        target = target,
        wide = true,
        plot_factual = true,
        img_height = 150
    )
    display(plt)
    push!(plts, plt)
end
```
